---
title: "Redistricting DAG"
subtitle: 
author:
output:
    # pdf_document:
    #   toc: true
    #   keep_tex: true
    html_document:
      highlight: zenburn
      #toc: true
      #toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

This “exploratory DAG” pulls nodes and edges from [this google sheet](https://docs.google.com/spreadsheets/d/13S_p2AY05PzPvUkp4t8xNW6xbefntktaGo9JAtfXw1Q/edit#gid=578039899). We can force these nodes into a hierarchy, but it is messier. I should be able to make a shiny app version of this that will allow us to select subsets of nodes from the google sheet--this will allow us to do all of our substantive edits in the google sheet and let this app render it for us.



```{r, include=FALSE}
# set working directory

library(tidyverse)
library(visNetwork)
library(igraph)
library(googlesheets4)
library(fontawesome)

knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)
```

```{r}
# refresh data from google sheet if token is present
if(gs4_has_token()){

ss <- googledrive::drive_get("redistricting vars") %>%
  gs4_get()
1
1

dag <- read_sheet(ss, "DAG") 

write_csv(dag, here::here("dag", "dag.csv"))
}

# load data
dag <- read.csv(here::here("dag", "dag.csv"))

# define function to plot
dag_plot <- function(dag){
node <- c(dag$from,
           dag$to)

nodes <- tibble(id = node %>% str_remove(".* - "),
                type = node %>% str_remove(" - .*")) %>% 
  filter(!is.na(id)) %>%
  distinct() %>%
    # removed nodes with multiple types
  add_count(id) %>% 
  filter(n == 1)

edges <- dag %>% transmute(
  from = from %>% str_remove(".* - "),
  to = to %>% str_remove(".* - "),
  detail = paste(edge, mechanism, cites, sep = "<br>") %>% str_remove_all("NA"), 
  type = edge
) %>% 
  filter(!is.na(from),!is.na(to)) %>% 
  distinct()



# calculate betweeness in order to scale nodes
graph <- igraph::graph.data.frame(edges, directed = T)
degree_value <- degree(graph, mode = "in")
nodes$icon.size <- degree_value[match(nodes$id, names(degree_value))] + 40

# add attributes
nodes <- nodes %>% mutate(label = id, 
                          title = paste0("<p>", type, ": ", label,"</p>"),
                          # levels in case we want Hierarchical Layout
                          level = ifelse(type == "goal", 1:2, 3:4),
                          # FontAwesome.com shapes for fun
                          shape = "icon",
                            icon.color = case_when(type =="goal" ~ "black",
                                                   type !="goal" ~ "black"),
                            icon.code = case_when(type == "condition" ~ "f205", # chess board
                                                  type == "goal" ~ "f24e", # scale  "f05b", # crosshairs
                                                  type == "policy" ~ "f0e3", # gavel
                                                  type == "value" ~ "f004", # "f4be", # hand with heart
                                                  type == "effect" ~ "f080", # "f681", # data 
                                                  type == "metric" ~ "f1de",# "f548", # ruler 
                                                  TRUE ~ "f0c8"), #square
                            icon.face =  "'FontAwesome'",
                            icon.weight = "bold")

# format edges
edges <- edges %>% mutate(
  title = paste0("<p>", detail, "</p>"),
  #label = type,
  color = ifelse(str_detect(type, "^increase"), "#81a275", "#617d9f"),
  color = ifelse(str_detect(type, "^decrease"), "#b14552", color) ) 



# make directed graph
visNetwork(nodes=nodes, edges=edges, width = "100%") %>% 
  visEdges(width=5, color= edges$color, arrows = "to", arrowStrikethrough = F, smooth = T) %>%
  visNodes(scaling=list(min=40, max=50)) %>%
  visOptions(highlightNearest = list(enabled = T, degree = 1, hover = T)) %>%
  visInteraction(hover=TRUE, zoomView = TRUE) %>%
  #visHierarchicalLayout() %>% 
  visPhysics(solver = "forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant = -50)) %>%
  addFontAwesome(name = "font-awesome-visNetwork") %>%
visLayout(randomSeed = 12) # to have always the same network  

# save datasets to call in Shiny
#save(nodes, file = here::here("dag", "nodes.RData"))
#save(edges, file = here::here("dag", "edges.RData"))

}
```

# The core nodes

```{r dag-core}
# plot core nodes
dag_plot(dag %>% filter(core) )
```

# The whole mess
```{r dag-whole}
# plot core nodes
dag_plot(dag)
```

