---
title: "How might redistricting affect representation?"
output: 
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(here)
library(broom)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>%  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

In addition to brainstorming possible dependent and explanatory variables in [this google sheet](https://docs.google.com/spreadsheets/d/13S_p2AY05PzPvUkp4t8xNW6xbefntktaGo9JAtfXw1Q), this pages describes possible designs to study the effects of redistricting. 

Assume continuous measures of representation, polarization, ideological extremity, in the range $\{0,1\}$ like those described in the "DVs" sheet. 

Also, assume a measure of partisan advantage, "packed" and "cracked" indicators, and other explanatory variables like those described in the "EVs" sheet.

# Are "packed" districts represented differently than other safe districts?

## Are representatives from packed districts less aligned with voters? 

Let $y_i$ be a measure of representation for official $i$.

Let $v_i$ be the margin of victory of official $i$ (or the margin for official $i$'s party in their district, etc.).

Let $p_i$ be an indicator of whether $i$'s district is packed. 

We can simulate data for a hypothetical set of safe districts (e.g., $v > 5%$). For illustration, I set the mean of $Y$ to .4 for packed districts and .6 for non-packed districts.

```{r rep_packed, fig.show='hold', out.width="40%", fig.width=3, fig.height=1.5}
packed <- tibble(packed = 1, 
                 vote_margin = sample(seq(5,45, 1), 
                                      100, 
                                      replace = T),
                 representation = rnorm(100, 
                                        .4, 
                                        .1))

notpacked <- tibble(packed = 0, 
                 vote_margin = sample(seq(5,45, 1), 
                                      100, 
                                      replace = T),
                 representation = rnorm(100, 
                                        .6, 
                                        .1))

d <- full_join(packed, notpacked)

ggplot(d) + 
  aes(x = representation, 
      fill = factor(packed)) +
  geom_histogram()

ggplot(d) + 
  aes(x = vote_margin, 
      fill = factor(packed)) +
  geom_histogram()
```

We can estimate representation given the vote margin and whether a district is packed, $y|p,v$


A linear fit would look like this: 

$\hat{y_i} = \beta_0 + \beta_1 p_i + \beta_2 v_i + \epsilon_i$

```{r rep_packed_model,fig.width=5, fig.height=3}
ggplot(d) +
  aes(x = vote_margin, 
      y = representation, 
      color = factor(packed)) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm") + 
  scale_color_viridis_d()
```

# Are representatives from packed districts more extreme?

Now let $y_i$ be a measure of ideological extremity.

We estimate ideological extremity given the vote margin and whether a district is packed $y|p,v$

```{r polar_packed, fig.show='hold', out.width="40%", fig.width=3, fig.height=1.5}
# d %<>% mutate(ideological_extremity = ifelse(packed == 1,...))
d$ideological_extremity <- rbeta(200, 1, 3)

ggplot(d) + 
  aes(x = ideological_extremity, 
      fill = factor(packed)) +
  geom_histogram()
```
A linear fit would look like this: 

$\hat{y_i} = \beta_0 + \beta_1 p_i + \beta_2 v_i + \epsilon_i$

```{r polar_packed_model,fig.width=5, fig.height=3}
m2 <- lm(ideological_extremity ~ packed + vote_margin,
         data = d)  %>% 
  augment(se_fit = T)

ggplot(m2) +
  aes(x = vote_margin, 
      y = ideological_extremity, 
      color = factor(packed),
      fill = factor(packed) ) + 
  geom_point(alpha = .2) + 
  geom_ribbon(aes(ymin = .fitted - .se.fit,
                  ymax = .fitted + .se.fit),
              alpha = .5,
              color = NA) + 
  geom_line(aes(y = .fitted)) + 
  scale_color_viridis_d()+ 
  scale_fill_viridis_d()
```

# Are "minimal secure margin" districts represented differently than other relatively secure districts?

Now consider the set of districts with voter splits like those engineered by a partisan gerrymander (margins $v$ about +5% for the advantaged party).  

We estimate ideological extremity given the vote margin and whether a district is packed $y|p,v$

$\hat{y_i} = \beta_0 + \beta_1 p_i + \beta_2 v_i + \epsilon_i$

# Are delegations from more gerrymandered states biased toward the advantaged party?

The aim of partisan gerrymandering is to shift politics in a state toward 

There are two sub-questions:

## Are advantaged delegations from more gerrymandered states biased toward the advantaged party?

## Are disadvantaged delegations from more gerrymandered states biased toward the advantaged party?

## Are black voters less well represented from cracked districts. From more gerrymandered states biased toward the advantaged party?


# Ideally, we want is counterfactual levels representation and polarization at different levels of partisan advantage

The level of partisan advantage is always confounded by time (in within-state) or state characteristics (in across-state analysis).








