---
title: "Representation by District"
subtitle: 
author: ""
output:
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>% 
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

# Member characteristics

## Congressional record parsed by speaker

Directory structure of the data/txt folder:
```{r}
cr_file <- list.files(here::here("data", "txt") %>% 
                        str_replace("redistricting", "Congressional records/cr"),
                      recursive = T) 

tibble(file = cr_file) %>% kablebox()
```


## Merge in voteview data

by Congress and legislator ICPSR identifier linking to variables including:

- DW-NOMINATE spatial ideology scores based on voting record (`nominate.dim1`, `nominate.dim2`)
- `party_size`

```{r}
d <- tibble(file = cr_file %>% str_remove(".*/"),
            speech_id = cr_file %>% str_extract("000[0-9]*"),
            icpsr = str_remove(cr_file, ".*-") %>% 
              str_remove(".txt") %>% 
              as.integer(),
            date = str_extract(cr_file, "CREC-[0-9]*-[0-9]*-[0-9]*") %>% 
              str_remove("CREC-") %>%
              as.Date) 

d %<>% filter(!is.na(icpsr))

# get congress from year 
d %<>% mutate(year = str_sub(date, 1,4) %>% as.integer()) # the 107th congress began in 2001

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))

d %<>% left_join(members) 

# count speeches per member
d %<>% group_by(icpsr) %>% add_count(name = "speeches_n") 

# drop name varients
d %<>% select(-contains("first"), -contains("common"), -contains("middle"), -contains("last"), -contains("maiden"), -pattern)

speeches <- d %>% distinct(icpsr, file, speech_id, speeches_n, date, year, congress, chamber, bioname)

d %>% 
  select(bioname, cqlabel, icpsr, file) %>% 
  distinct() %>% 
  kablebox()
```

---

## Subset to Wisconsin House Reps
```{r}
# House members from WI
d %<>% filter(state %in% c("wisconsin", "texas"),
             chamber == "House")




d %>% 
  select(bioname, cqlabel, icpsr, file) %>% 
  distinct() %>% 
  kablebox()
```


TODO

- [ ] identify WI House members who were up for reelection in 2020

- [ ] measure gregariousness (frequency of speeches)

- [ ] measure *level* of attention to their district (mentions of their home state, district, etc.)

- [ ] measure *ratio*/log odds of "my district" vs "my conscience" etc.

---

# District characteristics 

## Connectivity

- [Facebook friendships](https://github.com/judgelord/redistricting/blob/main/data/WI_congress_facebook_sci_pop.txt) (`facebook_sci`)
- [Travel](https://github.com/judgelord/redistricting/blob/main/data/district_flows_safegraph.txt) (`flow_count`)

We measure travel in two ways:

- Flows between districts (`flow_count`)
- Flows between districts from and two bordering census blocks, (`flow_count_border`)

> TODO: Add images illustrating these from Box

There are three values for each measure of connectivity:

- within-district 
- `out`-of-district 
- the `ratio` of within-district to out-of-district travel

```{r}
# facebook friend data
fb <- read_csv(here::here("data", "WI_congress_facebook_sci_pop.txt"))  %>% 
  mutate_all(as.integer) %>% 
  mutate(state = "wisconsin")

names(fb) %<>% str_remove("_C.*")

# cell phone mobility data
flow <- read_csv(here::here("data", "WI_DistrictFlows_January_2020.csv")) %>%
                   mutate(state = "wisconsin")  %>% 
  full_join(read_csv(here::here("data", "TX_DistrictFlows_January_2020.csv")) %>% 
              mutate(state = "texas"))

flow_border <- read_csv(here::here("data", "WI_DistrictFlows_BorderCBGs_January_2020.csv")) %>%
                   mutate(state = "wisconsin")  %>% 
  full_join(read_csv(here::here("data", "TX_DistrictFlows_BorderCBGs_January_2020.csv")) %>% 
              mutate(state = "texas")) %>% 
  rename(Flow_Count_Border = Flow_Count)

flow %<>% 
  full_join(flow_border) %>%
  mutate(OD_Pairs = OD_Pairs %>% str_remove_all("\\(|\\)")) %>% 
  separate(OD_Pairs, into = c("from", "to"), sep = ", ") %>% 
  mutate(across(c(from, to), as.integer))

# names to match facebook data
names(flow) %<>% str_to_lower()

c <- full_join(fb, flow)

c %>% kablebox()
```

### Merge in connectivity



```{r}
flow_within <- c %>% filter(from == to)

flow_out <- c %>% filter(from != to) %>%
  select(-to) %>%
  group_by(state, from) %>% 
  summarise_all(sum) 

flows <- full_join(flow_within, flow_out, by = c("state", "from"), suffix = c("", "_out")) %>%
  mutate(flow_ratio = flow_count/flow_count_out,
         flow_ratio_border = flow_count_border/flow_count_border_out,
         facebook_sci_ratio = facebook_sci/facebook_sci_out) %>% 
  rename(district_code = to)



d2 <- d %>% 
  left_join(flows) %>% 
  filter(!is.na(flow_count)) 

# number of speeches
d2 %>% distinct(bioname, cqlabel, 
                flow_count, flow_count_out, flow_count_border, flow_count, flow_count_border_out, flow_ratio_border, facebook_sci, facebook_sci_out,facebook_sci_ratio, speeches_n) %>% kablebox()
```

## Demographics

```{r}
dem <- read_csv(here::here("data", "CD_DEMO_DATA", "115CD_DEMOGRAPHIC_SUMMARY_ACS_2010_CENSUS_1YR_EST.csv"))

# the first 4 rows are metadata for values
dem_names <- head(dem, 4) 

# pivot value names
dem_names %<>% 
  mutate(NAME = c("format", "type", "measure", "group") ) %>%
  group_by(NAME) %>% 
  pivot_longer(!NAME) %>% 
  ungroup() %>% 
  pivot_wider(names_from = NAME)

# pivot data
dem %<>% 
  group_by(NAME, GEO_ID) %>%
  pivot_longer(starts_with("SF")) %>% 
  mutate(state = str_remove(NAME, ".*, ") %>% str_to_lower(),
         district_code = str_extract(NAME, "District [0-9]*") %>% 
           str_remove("District ") %>% as.numeric()) %>% 
  # drop non-values 
  mutate(value = as.numeric(value)) %>% filter(!is.na(value)) %>%
  #join value names
  left_join(dem_names) %>% 
  rename(district_name = NAME)

# demographic variables
dem %>% 
  distinct(type, measure, group) %>%
  kablebox()
```

### Merge in Census Demographics
```{r}
# join demographics to speech and community data
d2 %<>% left_join(dem) 

d2 %>% 
  filter(format == "Percent"#, type == "RACE"
         ) %>% 
  select(bioname, cqlabel, type,  group, measure, value, format) %>% 
  distinct() %>%
  kablebox()
```

---

## Partisanship

```{r}
partisanship <- read_csv(here::here("data", "WI_FULL_WARD_ELECTORAL_DATA_02_TO_18.csv")) %>% 
  mutate(district_code = CON %>% as.integer() ) %>% 
  select(-NAME) %>% 
  #FIXME these data are only for WI
  mutate(state = "wisconsin")

partisanship %>% kablebox()
```


### Aggregate to district 

```{r}
partisanship_agg <- partisanship %>% 
  group_by(state, district_code) %>% 
  # for example, sum cumulative patisanship vars
  summarise(across(contains("_CUM_") | PERSONS|BLACK|WHITE|HISPANIC| ASIAN|AMINDIAN, sum))

partisanship_agg %>% kablebox()
```
 
### Merge in aggregate partisanship
```{r}
d3 <- d2 %>% left_join(partisanship_agg) %>% arrange(desc(state))

d4 <- d3 %>%
  select(bioname, state, district_code, icpsr,
         # speech
         speeches_n, file,
         # community
         facebook_sci, flow_count,
         # race 
         PERSONS, BLACK, WHITE, HISPANIC, ASIAN, AMINDIAN,
         # partisanship
         starts_with("REP"), starts_with("DEM"), starts_with("OTH")) %>%
  distinct() %>% 
  ungroup()

d4 %>% 
  kablebox()
```


# Docs 

## Improve documentation by editing this [google sheet](https://docs.google.com/spreadsheets/d/1VLX92ZPPMFy3ypocym549vM82SyN27t51-cwcLfIacA)

```{r}
docs <- d2 %>% slice(2) %>%
  #FIXME when we figure out long/wide format 
  left_join(partisanship) %>% ungroup() %>% arrange(desc(state)) 

docs <- tibble(
  variable = names(docs),
  class = lapply(docs, class) %>%
    unlist(., use.names=FALSE),
  example = docs %>% slice(1) %>% 
    mutate_all(as.character()) %>%
    as.matrix() %>% c()
       ) 

# google doc
library(googlesheets4)
gs4_auth(email = "devin.jl@gmail.com")

docs_gs <- read_sheet("https://docs.google.com/spreadsheets/d/1VLX92ZPPMFy3ypocym549vM82SyN27t51-cwcLfIacA")

docs %<>% left_join(docs_gs %>% select(-class, -example))

sheet_write(docs,  "https://docs.google.com/spreadsheets/d/1VLX92ZPPMFy3ypocym549vM82SyN27t51-cwcLfIacA", "docs")


docs %>% 
  kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "600px")
```

# Toy Data

```{r}
member_district <- d4

# RDATA 
save(member_district, file = here::here("data", "member_district_example.Rdata"))

# CSV
write_csv(member_district, path = here::here("data", "member_district_example.csv"))

# SQLite database
library(DBI)
library(RSQLite)
con <- dbConnect(RSQLite::SQLite(), here::here("data", "member_district_example.sqlite"))

dbWriteTable(con, "members", members, overwrite = T)

dbWriteTable(con, "speeches", speeches, overwrite = T)

dbWriteTable(con, "connectivity", c, overwrite = T)

dbWriteTable(con, "demographics", dem, overwrite = T)

dbWriteTable(con, "partisanship", partisanship, overwrite = T)

# Example SQL fetch results:
speeches2020 <- dbGetQuery(con, "SELECT * FROM speeches WHERE year = '2020'") 
```

- [member_district_example.Rdata](https://github.com/judgelord/redistricting/blob/main/data/member_district_example.Rdata)
- [member_district_example.csv](https://github.com/judgelord/redistricting/blob/main/data/member_district_example.csv)
- member_district_example.sqlite (in dropbox; too large for github). SQL tables:

```{r}
dbListTables(con)
dbDisconnect(con)
```