---
title: "Representation by District"
subtitle: 
author: ""
output:
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>% 
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

# Congressional record parsed by speaker

## Directory structure

In the data/txt folder:
```{r}
cr_file <- list.files(here::here("data", "txt") %>% 
                        str_replace("redistricting", "Congressional records/cr"),
                      recursive = T) 

cr_file %>% kablebox()
```


## Merge in voteview data 

by legislator ICPSR id and congress

```{r}
d <- tibble(file = cr_file %>% str_remove(".*/"),
            speech_id = cr_file %>% str_extract("000[0-9]*"),
            icpsr = str_remove(cr_file, ".*-") %>% 
              str_remove(".txt") %>% 
              as.integer(),
            date = str_extract(cr_file, "CREC-[0-9]*-[0-9]*-[0-9]*") %>% 
              str_remove("CREC-") %>%
              as.Date) 

d %<>% filter(!is.na(icpsr))

# get congress from year 
d %<>% mutate(year = str_sub(date, 1,4) %>% as.integer()) # the 107th congress began in 2001

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))

d %<>% left_join(members)

d %>% 
  select(bioname, cqlabel, icpsr, file) %>% 
  distinct() %>% 
  kablebox()
```

---

## Subset to Wisconsin House Reps
```{r}
# House members from WI
d %<>% filter(state == "wisconsin",
             chamber == "House")


d %>% 
  select(bioname, cqlabel, icpsr, file) %>% 
  distinct() %>% 
  kablebox()
```


### TODO

- [ ] identify WI House members who were up for reelection in 2020

- [ ] measure gregariousness (frequency of speeches)

- [ ] measure *level* of attention to district (mentions of home state, district, etc.)

- [ ] measure *ratio*/log odds of "my district" vs "my conscience" etc.

# District characteristics 

## Connectivity

```{r}
# facebook friend data
fb <- read_csv(here::here("data", "WI_congress_facebook_sci_pop.txt"))  %>% 
  mutate_all(as.integer)

names(fb) %<>% str_remove("_C.*")

# cell phone mobility data
flow <- read_csv(here::here("data", "district_flows_safegraph.txt")) %>%
  mutate(OD_Pairs = OD_Pairs %>% str_remove_all("\\(|\\)")) %>% 
  separate(OD_Pairs, into = c("from", "to"), sep = ", ") %>% 
  mutate_all(as.integer)

names(flow) %<>% str_to_lower()

c <- full_join(fb, flow)

c %>% kablebox()
```

## Merge speeches and within-district connectivity
```{r}
within <- c %>% filter(from == to)


dc <- d %>% left_join(within,
                by = c("district_code" = "to")) %>% filter(!is.na(flow_count)) 

# number of speeches
dc %>% count(bioname, cqlabel, flow_count, facebook_sci, name = "speeches_n") %>% kablebox()
```

## Demographics

TODO

## Partisanship

TODO


